### 2025-11-05 simulation.qmd
20251105 - clarification of Monte Carlo simulation using SimDesign

@@

@@

For each player, we identify the optimal distribution as either a normal distribution , or as a skew-normal distribution.
The normal distribution was fit using the `fitdistrplus::fitdist()` function of the `fitdistrplus` package [@R-fitdistrplus; @DelignetteMuller2015_packages].
The skew-normal distribution was fit using the `sn::selm()` function of the `sn` package [@R-sn; @Azzalini2023_packages].

@@

Now we build the `SimDesign` design grid based on the number of projections that each player had.

@@

@@

@@

@@

Now, we can run the model using the `SimDesign::runSimulation()` function.

>>>>

In general, a Monte Carlo simulation study involves several steps:

1. generate the data for the simulation from the relevant probabilty distribution(s)
1. analyze the simulated data
1. summarize the results across the simulation replications

Below we conduct a Monte Carlo simulation to determine the range of each player's most likely points scored based on their projected points.
To do this, we use the `SimDesign` [@R-SimDesign; @Chalmers2020_packages] package.

@@

The `SimDesign` [@R-SimDesign; @Chalmers2020_packages] package uses a five-step process to perform Monte Carlo simulations:

1. Step 1—Design Grid: specify the fixed conditions to investigate in the simulation (e.g., sample size, generating distribution)
1. Step 2—Generate: specify how to generate the data for the simulation from the relevant probabilty distribution(s)
1. Step 3—Analyze: specify how to analyze the simulation data
1. Step 4—Summarize: specify how to summarize the results across the simulation replications
1. Step 5—Run the Simulation: run the simulation study (i.e., generate the data, analyze the simulated data, and summarize the results across the simulation replications)

@@

For each player, we identify the optimal distribution of their projected points across sources as either a normal distribution, or as a skew-normal distribution.
The normal distribution was fit using the `fitdistrplus::fitdist()` function of the `fitdistrplus` package [@R-fitdistrplus; @DelignetteMuller2015_packages].
The skew-normal distribution was fit using the `sn::selm()` function of the `sn` package [@R-sn; @Azzalini2023_packages].

@@

First, we define what combinations of conditions to study, which is called our design grid.
In our simulation study, each player retains the same number of projections as they had in the original data, ensuring the simulation reflects real-world variation in data availability.
This number of projections defines our design grid.

@@

Second, we generate the data for the simulation from the relevant probabilty distribution function(s).
In this case, we use a normal distribution or skew-normal distribution as our probability distribution function for a given player, depending on which distribution fits better to that player's distribution of projected points across sources (stored in `dist_info$type`).

@@

Third, we analyze the simulated data.

@@

Fourth, we summarize the results across the simulation replications.

@@

Fifth, we run the simulation study.
We run the simulation study using the `SimDesign::runSimulation()` function.
